---
title: "p8105_hw1_js5962"
author: "Jiayao Sun"
date: 2021-09-28
output: github_document
---

# Problem 1

* Create a data frame comprised of:
  * a random sample of size 10 from a standard Normal distribution
  * a logical vector indicating whether elements of the sample are greater than 0
  * a character vector of length 10
  * a factor vector of length 10, with 3 different factor “levels”

Solution :

1. create the data frame
```{r setup, include = FALSE}
library(tidyverse)
```

```{r df_create}
set.seed(1234)

hm1_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = c(vec_numeric > 0),
  vec_char = c("a", "b", "c", "d", "e", "f", "g","h", "i", "j"),
  vec_factor = factor(c("level 1", "level 2", "level 3", "level 1", "level 2", "level 3","level 1", "level 2", "level 3", "level 1"))
)
hm1_df
```

2. If we take the mean of each variable in your dataframe
```{r mean, echo = FALSE}
 mean(pull(hm1_df, vec_numeric))
 mean(pull(hm1_df, vec_logical))
 mean(pull(hm1_df, vec_char))
 mean(pull(hm1_df, vec_factor))
```

Thus the number and logical vectors works for mean. The characters and factors do not work.

3. Then we convert logical, character and factor vectors into numbers.
_Do not show the output_
```{r convert, results = 'hide'}
 x = as.numeric(pull(hm1_df, vec_logical))
 y = as.numeric(pull(hm1_df, vec_char))
 z = as.numeric(pull(hm1_df, vec_factor))
```

4. Take the mean again
```{r mean_convert, echo = FALSE}
 mean(pull(hm1_df, vec_numeric))
 mean(x)
 mean(y)
 mean(z)
```

After converting, the logical vector remains the same, which is **True = 1** and **False = 0**. The factor vector generates the numerical mean. But the character variable cannot be converted into numbers and are left as NA.

# Problem 2

1. Download the a package containing the penguins data set (done in console)
2. 
```{r penguine, results = 'hide'}
data("penguins", package = "palmerpenguins")
```

* The **Penguins data set** has the following variables: `r ls(penguins)`.

  * Bill depth (in mm), _the `r class(pull(penguins, bill_depth_mm))` variable_, has a mean of `r mean(pull(penguins, bill_depth_mm), na.rm=TRUE)`, a median of `r median(pull(penguins, bill_depth_mm), na.rm=TRUE)`, and a range of `r range(pull(penguins, bill_depth_mm), na.rm=TRUE)` (min, max).
  * Bill length (in mm), _the `r class(pull(penguins, bill_length_mm))` variable_, has a mean of `r mean(pull(penguins, bill_length_mm), na.rm=TRUE)`, a median of `r median(pull(penguins, bill_length_mm), na.rm=TRUE)`, and a range of `r range(pull(penguins, bill_length_mm), na.rm=TRUE)` (min, max).
  * Body mass (in g), _the `r class(pull(penguins, body_mass_g))` variable_, has a mean of `r mean(pull(penguins, body_mass_g), na.rm=TRUE)`, a median of `r median(pull(penguins, body_mass_g), na.rm=TRUE)`, and a range of `r range(pull(penguins, body_mass_g), na.rm=TRUE)` (min, max).
  * flipper_length (in mm), _the `r class(pull(penguins, flipper_length_mm))` variable_, has a mean of `r mean(pull(penguins, flipper_length_mm), na.rm=TRUE)` and a range of `r range(pull(penguins, flipper_length_mm), na.rm=TRUE)` (min, max).
  * Island, _the `r class(pull(penguins, island))` variable_, has `r levels(pull(penguins, island))` islands.
  * Sex, _the `r class(pull(penguins, sex))` variable_,  has `r levels(pull(penguins, sex))` categories.
  * Species, _the `r class(pull(penguins, species))` variable_, has `r levels(pull(penguins, species))` species.
  * Year, _the `r class(pull(penguins, year))` variable_. has a range of year `r range(pull(penguins, year))`.

The Penguin data set has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
The mean flipper length is `r mean(pull(penguins, flipper_length_mm).

3. Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x) and save it.
```{r scatterplot}
library(ggplot2)
set.seed(1234)
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() + ggtitle("Flipper Length(y) vs Bill Length(x)") + theme(plot.title = element_text(hjust = 0.6))
ggsave("scatterplot_Problem2.pdf")
```







