---
title: "p8105_hw1_js5962"
author: "Jiayao Sun"
date: 2021-09-28
output: github_document
---

# Problem 1

* Create a data frame comprised of:
  * a random sample of size 10 from a standard Normal distribution
  * a logical vector indicating whether elements of the sample are greater than 0
  * a character vector of length 10
  * a factor vector of length 10, with 3 different factor “levels”

Solution :

```{r setup, include = FALSE}
library(tidyverse)
```

```{r df_create}
set.seed(1234)

hm1_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = c(vec_numeric > 0),
  vec_char = c("a", "b", "c", "d", "e", "f", "g","h", "i", "j"),
  vec_factor = factor(c("level 1", "level 2", "level 3", "level 1", "level 2", "level 3","level 1", "level 2", "level 3", "level 1"))
)
hm1_df
```

If we take the mean of each variable in your dataframe
```{r mean, echo = FALSE}
 mean(pull(hm1_df, vec_numeric))
 mean(pull(hm1_df, vec_logical))
 mean(pull(hm1_df, vec_char))
 mean(pull(hm1_df, vec_factor))
```

Thus the number and logical vectors works for mean. The characters and factors do not work.

Then we convert logical, character and factor vectors into numbers.
_Do not show the output_
```{r convert, results = 'hide'}
 x = as.numeric(pull(hm1_df, vec_logical))
 y = as.numeric(pull(hm1_df, vec_char))
 z = as.numeric(pull(hm1_df, vec_factor))
```

Take the mean again
```{r mean_convert, echo = FALSE}
 mean(pull(hm1_df, vec_numeric))
 mean(x)
 mean(y)
 mean(z)
```

After converting, the logical vector remains the same, which is **True = 1** and **False = 0**. The factor vector generates the numerical mean. But the character variable cannot be converted into numbers and are left as NA.

# Problem 2

I can take the mean of the sample, too!






